---
title: "Homework4 Submission1"
author: "Moyo Odugbemi"
prefer-html: true
subtitle: "https://github.com/modugbe/homework4"
format: 
   pdf: 
     df-print: default
     output-file: "odugbemi-m-hwk4-1"
     output-ext: "pdf"
     header-includes:
        - \usepackage{float}
        - \floatplacement{table}{H}
---


```{r results="hide", echo=FALSE, message=FALSE}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra, webshot2, knitr)
```



```{r results="hide", echo=FALSE, message=FALSE}
#| include: false
#| eval: true
 
load("/Users/moyosoreoluwaodugbemi/Econ 470/Homework 4/submission1/Hwk4_workspace.Rdata")
```


\newpage
#Question 1
```{r results="hide", echo=FALSE, message=FALSE}
number1
```

\newpage
#Question 2
```{r results="asis", echo=FALSE, message=FALSE}
number2
```

\newpage
#Question 3
```{r results="hide", echo=FALSE, message=FALSE}
number3
```

\newpage
#Question 4
```{r results="hide", echo=FALSE, message=FALSE}
number4
```

\newpage
#Question 5
```{r results="hide", echo=FALSE, message=FALSE}
number5
```

\newpage
#Question 6

```{r results="asis", echo=FALSE, message=FALSE}
#number6
```


\newpage
#Question 7 
```{r results="hide", echo=FALSE, message=FALSE}
#number7
```
The rdplot has not rendered in quarto :(


\newpage
#Question 8 
```{r results="hide", echo=FALSE, message=FALSE}
#number8
```


\newpage
#Question 9 
```{r results="hide", echo=FALSE, message=FALSE}
#number9
```

\newpage
#Question 10
I'm assuming that the effect of increasing a star rating will lead to an increase in enrollments. At this point, I am unable to confirm with the findings from 5-9 as I have not yet organized those results. 
