---
title: "Homework4 Submission3"
author: "Moyo Odugbemi"
prefer-html: true
subtitle: "https://github.com/modugbe/homework4"
format: 
   pdf: 
     df-print: default
     output-file: "odugbemi-m-hwk4-3"
     output-ext: "pdf"
     header-includes:
        - \usepackage{float}
        - \floatplacement{table}{H}
---


```{r results="hide", echo=FALSE, message=FALSE}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra, webshot2, knitr)
```



```{r results="hide", echo=FALSE, message=FALSE}
#| include: false
#| eval: true
 
load("/Users/moyosoreoluwaodugbemi/Econ 470/Homework 4/submission3/Hwk4_workspace.Rdata")
```


\newpage
#Question 1
```{r results="hide", echo=FALSE, message=FALSE}
number1
```
What the plot shows is that there are some counties that have higher plan counts than others in a given year. I think making a judgement on the number of plans would require knowing the population of a county which affects the number of options people would need. Plan counts are lower in subsequent years than in 2010.

\newpage
#Question 2
```{r results="asis", echo=FALSE, message=FALSE}
number2
```
Distribution has shifted towards higher ratings over the years. Majority started in 2010 with 2.5 stars and that has become a majority with 4.0 ratings in 2015.

\newpage
#Question 3
```{r results="hide", echo=FALSE, message=FALSE}
number3
```
The average benchmark payment has decreased since 2010. Although there was a spiked increase in 2014, the total payment has changed by `r format(as.numeric(total_payment_increase, big.mark=",")

\newpage
#Question 4
```{r results="hide", echo=FALSE, message=FALSE}
number4
```

```{r results="asis", echo=FALSE, message=FALSE}
correlation
```


\newpage
#Question 5
```{r results="asis", echo=FALSE, message=FALSE}
#| echo: false
#| label: Star Rating Count
#| tbl-cap: "Star Rating Counts"

options(knitr.kable.NA = 0)
knitr::kable(number5, 
             booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))
```

\newpage
#Question 6

```{r results="hide", echo=FALSE, message=FALSE}
result_table6
```




\newpage
#Question 7 
```{r results="hide", echo=FALSE, message=FALSE}
number7
```



\newpage
#Question 8 
```{r results="hide", echo=FALSE, message=FALSE}
number8a
```


\newpage
#Question 9 
```{r results="hide", echo=FALSE, message=FALSE}
#number9
```

\newpage
#Question 10
I'm assuming that the effect of increasing a star rating will lead to an increase in enrollments. At this point, I am unable to confirm with the findings from 5-9 as I have not fully organized those results. 
